---
title: "p8105_hw1_smi2112"
output: github_document
---

# Question 1

Creating the data frame:

```{r}
library(tidyverse)

question_one_df <- tibble(
    random_samp = runif(10, min = 0, max = 5),
    logical_vec = random_samp > 2,
    char_vec = c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten"),
    factor_vec = factor(c("yes", "yes", "yes", "yes", "yes", "no",  "no", "no", "no", "no"))
)
```

Attempting to take the mean of each variable in the data frame:

```{r}
mean(question_one_df$random_samp)
mean(question_one_df$logical_vec)
mean(question_one_df$char_vec)
mean(question_one_df$factor_vec)
```

The mean of the random sample is `r mean(question_one_df$random_samp)`, and the mean of the logical vector is `r mean(question_one_df$logical_vec)`.

The mean of the random sample works because the vector is made up of numbers generated by the runif() function, and r is able to take the mean of numbers. The mean of the logical vector also works because the logical vector codes TRUE statements as 1 and FALSE statements as 0. The mean of the 1's and 0's is taken.

The mean of the character vector and the factor vector do not work becuase they are not numbers.











